### 2021-08-29 response_to_review.Rmd

# Reviewer: 1

- Overall, there is nothing wrong in the article, but lots of language issues, problems with references, and a few aspects of tours (including software and references) that have not been explored in detail. Please see the attached markup for details.

- Before submitting the revision, I would encourage one of the senior native English speaking authors to carefully do a final language review of the article. I have marked many language problems, but there may be more.

## Marked up comments

- check your citation settings; I would have expected that clicking on a citation brings you to that reference in the reference list, but this does not seem to be the case here

    - **This might be a problem with the Wiley template**

- "means" sounds strange; perhaps "refers to the number of dimensions in ..." ?

    - **Changed**

- first introduce "one-dimensional (1D) through to five-dimensional (5D)"; then you can use 1D, ..., 5D

    - **Changed**

- perhaps "As the dimension increases, ..."

    - **Changed**

- change to  "a 2D cube consists of ..." and "a 3D cube consists of ..."

    - **Changed**

- fig 1: explain how the cube doubles: by connecting the vertexes of the two cubes. can you use 3 colors: two colors for the two original cubes and a third color for the connecting edges of the vertexes; perhaps draw those connectors as dashed lines

- p2 l49: perhaps "seen that as the dimension increases by one, ..."

- p3 l14 just "e.g.," or "see for example"

- p3 l14 mention the underlying software as well (and then cite these references)

- p3 l16 what are geodesic interpolations? explain in 1 or2 sentences and add a reference

- p3 l17 "a multivariate ..." or "distributions"

@@

- I highly appreciate the specification of notations in Section 2.1, but few sections use the notation.  Instead, different tour methods are only described in text. 
I anticipate that the readers would benefit from a highlight of key differences between different tour variants and interactions using the unified notations. For example, (as far as I understand) guided tour finds a sequence of interesting projections $A_i$ by applying projection pursuit optimization on a predefined criteria $c(\cdot)$ of ``interestingness'' of a projection, $argmax_A c(XA)$; local tour rocks back and forth from a particular plane $A$ to randomly chosen targets $A_i$ in a small neighborhood $\{A_j |\; d(A_j, A) < \epsilon \}$; manual tour manipulates the contribution of any variable by editing the corresponding row $A[i]$ in the projection frame $A$, $A[i] \leftarrow A[i] + \Delta[i]$ and re-orthonormalizing the columns.

    - **Done**

- Section 2.2: "A guided tour ... The little tour ... and a local tour ..." --- cite?

    - **Done, cited as much as is possible. There isn't a good citation for little tour or local tour, so we have referred to the original Dataviewer software.**

### 2021-08-29 paper.Rmd
working on reviewer 2 suggestions

The term "high-dimensional" here means Euclidean space. Figure \ref{fig:cubes} shows a way to imagine this. It shows a sequence of cube wireframes, ranging from 1D through to 5D, where beyond 2D is a linear projection of the cube. As dimension increase, a new orthogonal axis is added. For cubes, this is achieved by doubling the cube: a 2D is two 1D cubes, a 3D is two 2D cubes, and so forth.

>>>>

The term "high-dimensional" here refers to the  dimensionality of the Euclidean space. Figure \ref{fig:cubes} shows a way to imagine this. It shows a sequence of cube wireframes, ranging from one-dimensional (1D) through to five-dimensional (5D), where beyond 2D is a linear projection of the cube. As the dimension increases, a new orthogonal axis is added. For cubes, this is achieved by doubling the cube: a 2D cube consists of two 1D cubes, a 3D cube consists of two 2D cubes, and so forth.
